Chr2 hotspot preliminary analyses

### 2019-06-27 analysis/paper/Chr11-prelim.Rmd
added 2 by 2 tables

>>>>

## 2 x 2 tables

```{r define_foo}
foo <- mylist %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  left_join(tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id) 
```

We binarize the continuum of mediation LOD difference values and that of pleiotropy test statistics.

```{r 2x2_table}
mediation_threshold <- 1.5
mediation_threshold_proportion <- 0.5
pleiotropy_threshold <- 4
table(med = foo$lod_diff > mediation_threshold, pleio = foo$pleiotropy_lod <= pleiotropy_threshold)
```

```{r make_mylist}
med_vals <- 2 * (1:5)
pleio_vals <- 2 * (2:5)
mylist <- list()
for(i in 1:length(med_vals)){
  my_other_list <- list()
  for (j in 1:length(pleio_vals)){
    uniq_cts_nonlocal <- foo %>% 
      mutate(med = lod_diff > med_vals[i], pleio = pleiotropy_lod <= pleio_vals[j]) %>%
      group_by(med, pleio) %>%
      select(nonlocal_gene_id, med, pleio) %>%
      unique() %>%
      count() %>%
      rename(n_unique_nonlocal_gene_id = n)
    uniq_cts <- foo %>% 
      mutate(med = lod_diff > med_vals[i], pleio = pleiotropy_lod <= pleio_vals[j]) %>%
      group_by(med, pleio) %>%
      select(local_gene_id, med, pleio) %>%
      unique() %>%
      count() %>%
      rename(n_unique_local_gene_id = n) %>%
      left_join(uniq_cts_nonlocal, by = c("pleio", "med"))

    my_other_list[[j]] <- foo %>%
      mutate(med = lod_diff > med_vals[i], pleio = pleiotropy_lod <= pleio_vals[j]) %>%
      group_by(med, pleio) %>%
      count() %>%
      left_join(uniq_cts, by = c("med", "pleio"))
  }
  mylist[[i]] <- my_other_list
} 
mylist
```

```{r}
mylist %>%
  map_df(bind_rows)
```

```{r}
mylist %>%
  map_df(bind_rows) %>%
  filter(as.logical(med), !as.logical(pleio))
```

```{r}
mylist %>%
  map_df(bind_rows) %>%
  filter(as.logical(med), as.logical(pleio))
```

```{r 2x2_table_proportion}
table(med = foo$lod_diff_proportion > mediation_threshold_proportion, pleio = foo$pleiotropy_lod <= pleiotropy_threshold)
```

```{r counts_lod_diff}
foo %>%
  filter(lod_diff > mediation_threshold, pleiotropy_lod <= pleiotropy_threshold) %>%
  group_by(local_symbol) %>%
  count() %>%
  arrange(desc(n))

```{r counts_lod_diff_prop_first}
foo %>%
  filter(lod_diff_proportion > mediation_threshold_proportion, pleiotropy_lod <= pleiotropy_threshold) %>%
  group_by(local_symbol) %>%
  count() %>%
  arrange(desc(n))

```{r counts_both}
foo %>%
  filter(lod_diff > mediation_threshold, lod_diff_proportion > mediation_threshold_proportion, pleiotropy_lod <= pleiotropy_threshold) %>%
  group_by(local_symbol) %>%
  count() %>%
  arrange(desc(n))
```

```{r counts_either}
foo %>%
  filter(lod_diff_proportion > mediation_threshold_proportion | lod_diff > mediation_threshold, pleiotropy_lod <= pleiotropy_threshold) %>%
  group_by(local_symbol) %>%
  count() %>%
  arrange(desc(n))

```{r counts_lod_diff_prop}
foo %>%
  filter(lod_diff_proportion > 0.2, pleiotropy_lod <= pleiotropy_threshold) %>%
  group_by(local_symbol) %>%
  count() %>%
  arrange(desc(n))

### 2019-06-27 analysis/paper/Chr2-prelim.Rmd
added 2 by 2 tables

```{r, load_attie}
load("~/Box Sync/attie/keller2018-chr2-hotspot-chtc/data-to-ignore/Attie_DO378_eQTL_viewer_v1.Rdata")
ls()
library(tidyverse)
```

@@

```{r load_dendextend}
suppressPackageStartupMessages(library(dendextend))
```

@@

@@

```{r 2x2_table_proportion}
table(med = foo$lod_diff_proportion > 0.4, pleio = foo$pleiotropy_lod <= pleiotropy_threshold)
```

@@

```{r counts_more}
foo %>%
  filter(lod_diff_proportion > 0.2, pleiotropy_lod <= pleiotropy_threshold) %>%
  group_by(nonlocal_symbol) %>%
  count() %>%
  arrange(desc(n))
foo %>% 
  filter(lod_diff_proportion > 0.2, pleiotropy_lod <= pleiotropy_threshold) %>%
  select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff_proportion, lod_diff)
  arrange(desc(nonlocal_symbol)) 
```

>>>>

```{r, load_attie}
load("~/Box Sync/attie/keller2018-chr2-hotspot-chtc/data-to-ignore/Attie_DO378_eQTL_viewer_v1.Rdata")
ls()
library(tidyverse)
options(tibble.print_max = 50, tibble.print_min = 20)
```

@@

@@

```{r make_mylist}
med_vals <- 2 * (1:5)
pleio_vals <- 2 * (2:5)
mylist <- list()
for(i in 1:length(med_vals)){
  my_other_list <- list()
  for (j in 1:length(pleio_vals)){
    uniq_cts_nonlocal <- foo %>% 
      mutate(med = lod_diff > med_vals[i], pleio = pleiotropy_lod <= pleio_vals[j]) %>%
      group_by(med, pleio) %>%
      select(nonlocal_gene_id, med, pleio) %>%
      unique() %>%
      count() %>%
      rename(n_unique_nonlocal_gene_id = n)
    uniq_cts <- foo %>% 
      mutate(med = lod_diff > med_vals[i], pleio = pleiotropy_lod <= pleio_vals[j]) %>%
      group_by(med, pleio) %>%
      select(local_gene_id, med, pleio) %>%
      unique() %>%
      count() %>%
      rename(n_unique_local_gene_id = n) %>%
      left_join(uniq_cts_nonlocal, by = c("pleio", "med"))

    my_other_list[[j]] <- foo %>%
      mutate(med = lod_diff > med_vals[i], pleio = pleiotropy_lod <= pleio_vals[j]) %>%
      group_by(med, pleio) %>%
      count() %>%
      left_join(uniq_cts, by = c("med", "pleio"))
  }
  mylist[[i]] <- my_other_list
} 
mylist
```

```{r}
mylist %>%
  map_df(bind_rows)
```

```{r}
mylist %>%
  map_df(bind_rows) %>%
  filter(as.logical(med), !as.logical(pleio))
```

```{r}
mylist %>%
  map_df(bind_rows) %>%
  filter(as.logical(med), as.logical(pleio))
```

@@

@@

## More figures

Let's plot a matrix of pleiotropy test statistics for nonlocal - local pairs, ordered by local gene's chromosomal position (ie, coordinate of the middle of the gene per ENSEMBL). We could, for example, color cells by pleiotropy test statistic value. Maybe truncate for those over 10.

## Still more figures: graph theory package

Can we represent, say, the collection of nonlocal traits in an undirected graph theory graph? We might say that nodes i and j are connected by an edge if they are both pleiotropic in pairwise tests with a single local trait.

```{r load_hotspots}
library(hotspots)
```

```{r}
mymat <- foo %>%
  tibble_to_matrix() %>%
  t() %>%
  (function(mat) mat <= 4) %>%
  make_adjacency_matrix()
myg <- mymat %>%
  igraph::graph_from_adjacency_matrix(mode = "undirected", weighted = TRUE, diag = FALSE) 
comm2 <- igraph::fastgreedy.community(myg)
```

### Find communities

```{r}
library(igraph)
```

```{r}
comm <- foo %>%
  tibble_to_matrix() %>%
  t() %>%
  make_adjacency_matrix() %>%
  igraph::graph_from_adjacency_matrix(mode = "undirected", weighted = TRUE, diag = FALSE) %>%
  fastgreedy.community()
